Stack Safety as a Security Property

### 2020-06-05 main.tex
CP - intro words

\begin{figure}
  \begin{minipage}{\textwidth}
  \begin{center}
$\cdots$
\memory{4}{gray}%
\memory{8}{green}[{\makebox[0pt]{Caller}}]%
\memory{4}{yellow}[{\makebox[0pt]{Args}}]%
\memory{8}{red}[{\makebox[0pt]{Callee}}]%
\memory{4}{gray}%
~$\cdots$
  \end{center}
  \end{minipage}\\
~\\
~\\
  \begin{minipage}{0.45\textwidth}
    \begin{center}
      Code 1
    \end{center}
  \end{minipage}~
  \begin{minipage}{0.45\textwidth}
    \begin{center}
      Code 2
    \end{center}
  \end{minipage}
  \caption{Examples of Unsafe Programs}
  \label{fig:stackunsafety}
\end{figure}

Everybody likes stack safety. Nobody can say what it is precisely.

The intention is to protect callers from callees.

Examples of what it isn't in the literature.
Small bad examples of things that can go wrong.

Turn this into a positive security property: integrity + confidentiality.

\leo{Variations of these should probably go here:}
    {\it Eager stack integrity} states that if a function call returns, the caller's stack data
    will be identical to what it was before the call. This implies the weaker {\it observable
    stack integrity}, which states that any changes to the caller's frame will produce the same
    observable behavior.

    Confidentiality is in the style of noninterference, defined on a per-call basis. For each call,
    the caller's data and the uninitialized stack do not interfere with observable behavior until return.
    In {\it eager stack confidentiality} this means that when a function is called, the memory outside of
    its stack frame could be scrambled without changing its observable behavior or the changes it makes
    to the program state. This implies the weaker {\it observable stack confidentialty} in which
    inaccessible memory could be scrambled at each call and restored on return without changing the
    observable behavior of the remaining program.

Challenges?
Shifting notion of who the attacker is throughout execution.

>>>>

\newcommand*{\MemoryLabel}[3]{\raisebox{#2}{\makebox(0,0){\hspace{#1}#3}}}

\begin{figure}
  \begin{minipage}{\textwidth}
    \begin{center}
\MemoryLabel{10em}{1.5em}{40}
\MemoryLabel{16em}{1.5em}{60}
\MemoryLabel{22em}{1.5em}{80}      
$\cdots$
\memory{4}{gray}%
\memory{5}{green}[{\makebox[0pt]{Caller}}]%
\memory{5}{yellow}[{\makebox[0pt]{Args}}]%
\memory{8}{red}[{\makebox[0pt]{Callee}}]%
\memory{4}{gray}%
~$\cdots$\\
  \end{center}
  \end{minipage}\\
~\\
~\\
  \begin{minipage}{0.45\textwidth}
    \begin{center}
\begin{verbatim}
jal ...
lw r1 r0 40 
\end{verbatim}
    \end{center}
  \end{minipage}~
  \begin{minipage}{0.45\textwidth}
    \begin{center}
\begin{verbatim}
jal ...
sw r0 r0 40 
\end{verbatim}
    \end{center}
  \end{minipage}
  \caption{Examples of Unsafe Programs}
  \label{fig:stackunsafety}
\end{figure}

\leo{I hate the writing here, but I wanted to make a start.}  The call
stack is an increasingly popular target for attacks exploiting memory
safety vulnerabilities, with potential consequences ranging from
attackers reading or corrupting private stack data, to highjacking a
programs control flow. To prevent such attacks, many techniques have
been proposed in the literature\leo{cite, point out? stack canaries,
  cherry, nicks...} aiming to achieve {\em stack safety}.

But what does stack safety even mean? A formal definition of stack
safety is missing from the literature, with the notion only being
defined negatively: through examples of stack unsafety. Two classical
examples of stack unsafety appear in Figure~\ref{fig:stackunsafety}.
\leo{Goal: on the left, a bad read; on the right, a bad right.}

A common undertone in such examples is the intention to protect
callers from callees: a callee should be not be able to access or
overwrite a caller's private data. In this paper we turn this
intuition into a formal security property, with an integrity and
a confidentiality component.

Informally, {\em stack integrity} guarantees that if a function call
returns, the caller's stack data will be identical to what it was
before the call. {\em Stack confidentiality} ensures that a callee's
observable behavior is not affected by memory outside its stack frame
(e.g. a caller's private data or uninitialized memory).

While integrity and confidentiality are relatively standard security
properties, this setting provides an interesting additional challenge:
the notion of who the attacker shifts throught execution. Not only
does a caller need to be protected from its callee, but the callee
itself needs to be potentially proteced from {\em its} callees.
